Cover letter for the original IJRR submission

### 2017-04-20 body/appendix_algo.tex
final version ?

First, we define an abstract structure State,
that describes a contact configuration.
The use of queues allows a FIFO approach regarding the order 
in which contacts are tested: we try to replace older contacts first when necessary.
Thus the algorithm is deterministic even though it can handle acyclic motions.

@@

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
If \textsc{GenFullBody} failed in achieving this, the method \textsc{RepositionContacts} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.

The pseudo code for the method \textsc{GenFullBody} is given by Algorithm~\ref{alg:pi}.

>>>>

First, we define an abstract structure State,
that describes a contact configuration.
The use of queues allows a FIFO approach regarding the order 
in which contacts are tested: we try to replace older contacts first when necessary.
Thus the algorithm is deterministic even though it can handle acyclic motions. \\

@@

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
Otherwise, the method \textsc{RepositionContacts} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.
Algorithm~\ref{alg:pi} gives the pseudo code for \textsc{GenFullBody}.
